|

### 2023-05-12 paper/01-introduction.Rmd
more intro

Officially tracked by the NFL since 1982, the most well-known statistic for evaluating defensive linemen on pass rushing plays is the sack.
A sack is recorded when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.
Sacks represent a simple binary measure of success for a rusher on a pass play.
However, there are many intermediate outcomes for a rusher that can also be considered successes that do not result in a sack.
Measures such a hits and hurries are collected by various outlets where hits counts the number of times a QB is hit while passing and hurries counts how often a QB has to throw the ball earlier than they would have liked to.

@@

The sum of sacks, hits, and hurries has been defined as "pressures" and is an improvement over sacks, but suffers from problems of subjectivity (e.g. was the play actually a hurry?) and are still binary outcomes (i.e. There is a continuum of plays that aren't hurries that all counted as simply "not hurries").

@@

Pro football focus (PFF) comes up with a metric called "pass-rush productivity" (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a slight improvement to pressures.
However, the choice of weights is ad-hoc and still only measures binary outcomes similar to the shortcomings of previously discussed metrics.

@@

More recently metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) [@Burke2018Created] have also been proposed and are substantial improvements over the less sophisticated counting statistics.
Nevertheless, these are still imperfect measures.
TIP is highly context dependent, as it can be influenced by the type of passing route (e.g. deep versus shallow).
PRWR is based on whether a pass rusher is able to beat their block before a fixed time (ESPN chooses 2.5 seconds) from the snap, but this is highly dependent on the rather arbitrary choice of time used to define a "win".
In addition, once a cut-off is chosen, this metric becomes binary like most of the previously discussed measures.

@@

@@

@@

The remainder of this paper is outlined as follows.
We first describe the player tracking data provided by 2023 Big Data Bowl in Section \ref{sec:data}.
We then introduces the formal definition of our metric STRAIN and our modeling approach in Section \ref{sec:methods}.
We present an real-game illustration of the proposed metric and study its performance in Section \ref{sec:results}.
We close with a discussion of future directions for STRAIN in Section \ref{sec:discussion}.

>>>>

Perhaps the most commonly-known statistics for evaluating defensive linemen on pass rush plays are sacks, hits, and hurries, which are observed at the discrete play-level.
Officially tracked by the NFL since 1982, a sack is recorded when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.
Sacks represent a simple binary measure of success for a rusher on a pass play.
However, there are many intermediate outcomes for a rusher that can also be considered successes that do not result in a sack.
Other traditional box-score statistics such hits and hurries are collected by various outlets where hits counts the number of times a QB is hit while passing and hurries counts how often a QB has to throw the ball earlier than they would have liked to.
The sum of sacks, hits, and hurries has been defined as "pressures" and is an improvement over sacks, but suffers from problems of subjectivity (e.g. was the play actually a hurry?) and are still binary outcomes (i.e. There is a continuum of plays that aren't hurries that all counted as simply "not hurries").
Pro football focus (PFF) comes up with a metric called "pass-rush productivity" (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a slight improvement to pressures.
However, the choice of weights is ad-hoc and still only measures binary outcomes similar to the shortcomings of previously discussed metrics.

@@

@@

@@

More recently proposed metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) [@Burke2018Created] are substantial improvements over the less sophisticated counting statistics.
Nevertheless, these are still imperfect measures.
TIP is highly context dependent, as it can be influenced by the type of passing route (e.g. deep versus shallow).
PRWR is created using player tracking data, which is at a more granular level than previous measures.
It demonstrates whether a pass rusher is able to beat their block before a fixed time (ESPN chooses 2.5 seconds) from the snap.
This is highly dependent on the rather arbitrary choice of time used to define a "win".
In addition, once a cut-off is chosen, this metric converts continuous data to a win/loss indicator, becoming binary like most of the previously discussed measures.

@@

<!-- https://www.taylorfrancis.com/chapters/edit/10.1201/9781315166070-12/forecasting-performance-college-prospects-selected-national-football-league-draft-julian-wolfson-vittorio-addona-robert-schmicker -->

@@

<!-- The academic literature on the performance of linemen, either offensive or defensive in football is scant. @AlamarGould2008 studied the the relationship between pass completion rate and performance of offensive linemen in terms of how successful they were at blocking.  The data for this study was collecting essentially by hand by watching and charting the performance of each lineman on a play.  This was done using games from the beginning 2007 season for seven teams and their first three games each.  The authors note that there is not much research on linemen saying "One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman."  -->

<!-- Later, @AlamarGoldner2011 again studied offensive linemen performance.  They analyzed 20 teams during the 2010 season for a total of 1,259 plays.  They don't estimate the performance of an individual lineman, but rather positions on a team (e.g. Chicago Bears' left tackle, Pittsburgh Steelers' center, etc.).  They then go on to use a survival analysis model to estimate time in pocket.  The average probability of success from the survival model is then used as a covariate in a model to estimate the probability of competing a pass, and they show that there is a significant relationship between these two probabilities.   -->

@@

The remainder of this paper is outlined as follows.
We first describe the player tracking data provided by 2023 Big Data Bowl in Section \ref{sec:data}.
We then introduces the mathematical motivation and definition of our metric STRAIN and our modeling approach in Section \ref{sec:methods}.
We present an real-game illustration of the proposed metric and study its performance in Section \ref{sec:results}.
We close with a discussion of future directions for STRAIN in Section \ref{sec:discussion}.
